%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lawrence Livermore National Laboratory} % Organization   
    {Computation Student Intern} % Job title
    {Livermore, USA} % Location
    {Summer 2018, 2019 \& 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and develop CallFlow, an interactive visual analysis tool that provides a high-level overview of Calling Context Tree (CCT) together with semantic refinement operations to progressively explore the CCTs.} 
        \item {Designed new visualization tools and techniques to identify bottlenecks in the application code during performance analysis.}
        \item {Designed visualization encodings to help compare performance profiles and study performance variability across multiple executions of a HPC application.}
        \item{Collaborated with HPC experts to diagnose load balancing problems for acheiving scalable performance of scientific applications.}
      \end{cvitems}
    }
    
  \cventry
    {UC Davis} % Organization
    {Graduate Research Assistant - VIDI labs} % Job title
    {Davis, USA} % Location
    {June 2017 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Created visual interfaces to handle performance analysis of HPC performance data, such as calling contexts, network communication, and hardware event logs.}
        \item{Designed a block-based visualization technique to perform intuitive temporal event sequence analysis on hundreds of electronic health records.}
        \item {Integrate visual analytics frameworks for analyzing network communication in large-scale HPC applications produced by parallel discrete-event simulations (PDES).}
        \item {Introduce a visual analytics framework for analyzing in-situ performance data in real-time by preserving user's mental map during analysis.}
      \end{cvitems}
    }
    
  \cventry
    {University of California, Davis} % Organization
    {Teaching Assistent} % Job title
    {Davis, USA} % Location
    {Fall 2017, Winter 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {ECS 60. Data Structures \& Algorithms.}
        \item {ECS 122A. Algorithm Design \& Analysis.}
      \end{cvitems}
    }


%---------------------------------------------------------

  \cventry
    {DeltaForce - Web team and programming club of NIT Trichy} % Organization
    {Student System Administrator} % Job title
    {Tiruchirappalli, India} % Location
    {2013 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a project to establish a peer-to-peer service to share files over network using ADC (Advanced Direct Connect) protocol.}    
        \item {Managed college web servers to handle concurrency and diagnosed network security issues.}
        \item {Developed a C-library to perform static malware analysis for ELF binaries.}
        % \item {Participated in multiple hackathons and capture the flag (CTF) events representing NITT.}
      \end{cvitems}
    }



  \cventry
    {SportsCafe} % Organization
    {Full Stack Engineer Intern} % Job title
    {Bangalore, India} % Location
    {Summer 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Designed RESTful APIs to help scorers provide real-time updates using Javascript, React, HTML and CSS.}
        \item{Configured a Continuous Integration (CI) environment to automate deployment to Amazon's AWS services (including EC2, ECS, S3).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Paperhut - } % Organization
    {Software Engineer Intern} % Job title
    {Chennai, India} % Location
    {Summer \& Winter 2015} % Date(s)
    {
      \begin{cvitems}
        \item{Developed an NLP models to predict answers for a question asked from a structured textbook using NLTK.}
        \item{Built a pipeline to process PDF files to categorize text into chapters using Python.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
